\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-29 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent This is a very important point we had not thought about, and we thank the referee for raising it.
The referee definitely has a point here, in the sense that Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
To that extent, the findings in \cite{Lashkaripour_JIE2020} were an eye-opener.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production.  \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs.
This result of transport costs close to be totally iceberg contrasts from our own findings of additive costs representing 30 to 45\% of total costs.
We believe the two sets of findings are complementary.

We now report results based on per-unit prices.
They confirm the results of \cite{Lashkaripour_JIE2020}
Yet, first, looking at per-unit prices leads to leaving aside a large part of the data, both sectorally and chronologically.
Second,  it is interesting to look at additive costs on a per-weight basis even there is a correlation between unit price and weight.

@@

The same issue imposes the use of (sector,quantity unit) fixed effect rather than sector fixed effects
But this is not enough to adapt our equation to unit prices rather than weight price.
As discussed above, in our baseline regression we separate each transport cost component in its two distinct sector-origin country dimensions.
As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector.
In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects.
Sector-level fixed effects can be easily replaced by (sector,quantity unit) fixed effects.
But the same is not possible for country fixed effects.
In the per-weight price, the existence of a single country fixed effect applicable to all sector could be justified, as a kilogram is always a kilogram and one can assume they both add the same to transport from, say, Germany.
But a unit of tee-shirt is quite different from an unit of car.
Assume imports of tee-shirts and cars from Germany and China.
Importing a tee-shirt from either country implies paying the fixed effect for both countries (the same for all sectors) and the fixed effect for the sector (the same for all countries).
Idem for importing a car.
Hence, the difference in the cost of importing a car from Germany and the cost of importing a car from China would be the same (in dollars) as difference between the cost of importing a tee-shirt from Germany and the cost of importing a tee-shirt from China.
This does not seem to us as a reasonable assumption; in this case specifically, we cannot keep the separability assumption.
As discussed before, that dramatically increases the computational difficulty of our method and yet does not yield different results.

\subsubsection{Estimation}

As a consequence, we run the following estimation on a reduced sample (2009-2019, 66\% of the value of the baseline sample)

@@

\begin{equation}
\ln\left(\frac{p_{ik}}{p^u_{ik}}-1 \right)= \ln \left(\tau_{is(k)} -1+\frac{t_{is(k)} }{p^u_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
\noindent where $p^u_{ik}$ refers to the unit price associated with quantity. Depending on the sector, two different units are considered, kilograms and numbers.

These results, in the online appendix, Section D.4, Table D.2 and Figure D.4\textbf{XXX CHECK XXX }. For sake of reading clarity, we report here the results of Table D.2 (Table \ref{tab_comp_wgt_qty} here and figure \ref{graph_comp_wgt_qty} ). For each transport mode, the first column reports the estimation based on the price per quantity; while the second column reports the results obtained considering the price per kg on the same sample; the last column reported our baseline results on the large sample (considering the average value over 2009-2019).

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

These results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air).
They confirm the results of \citet{Lashkaripour_JIE2020} that there is a correlation between weight per unit and unit price.
Still, the share of additive cost is not reduced to zero, except if one looks at the median for vessel).
Thus these results do not disqualify our approach, especially as we cover a much larger period and sample.

\subsubsection{Why is price per weight interesting}
It is true that to study welfare, the relevant variable that would create distortions is the cost per unit. 
However, our primary aim is descriptive. 
From that point of view, transport cost schedule are expressed historically and currently in a mix per-weight and per-volume basis. 
Fo example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight’’ or ``dimensional weight). See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).
Maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors.
The existence of per-volume or per-weight shipping cost is a fact of (second) nature, directly linked to the technical constraints of the transportation sector.

The notion of per-unit shipping cost is one step removed for technical constraints and the functionning of the transportation sector.
The weight per unit is at least partly the result of a choice by firms.

### 2021-10-30 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

        From this, we can deduce the confidence interval $CI^{ref}_{is} = \hat{\beta}_{is}^{max,ref} - \hat{\beta}_{is}^{min,ref}$.

        \item  Our method provides estimates of the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We then deduce the accuracy of the $\beta$ estimate by relying on bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 threshold values for each couple $i,s$. Noticing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the referee's method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.

@@

These results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air).
They confirm the results of \citet{Lashkaripour_JIE2020} that there is a correlation between weight per unit and unit price.
Still, the share of additive cost is not reduced to zero, except if one looks at the median for vessel).
Thus these results do not disqualify our approach, especially as we cover a much larger period and sample.

\subsubsection{Why is price per weight interesting}
It is true that to study welfare, the relevant variable that would create distortions is the cost per unit. 
However, our primary aim is descriptive. 
From that point of view, transport cost schedule are expressed historically and currently in a mix per-weight and per-volume basis. 
Fo example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight’’ or ``dimensional weight). See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).
Maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors.
The existence of per-volume or per-weight shipping cost is a fact of (second) nature, directly linked to the technical constraints of the transportation sector.

The notion of per-unit shipping cost is one step removed from technical constraints and the functionning of the transportation sector.
The weight per unit is at least partly the result of a choice by firms. 
To understand the context in which they operate, we find that studying the technical per-volume or per-weight shipping cost is interesting.

### 2021-10-31 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

These results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air).
They confirm the results of \citet{Lashkaripour_JIE2020} that there is a correlation between weight per unit and unit price.
Still, the share of additive cost is not reduced to zero, except if one looks at the median for vessel).
Thus these results do not disqualify our approach, especially as we cover a much larger period and sample.

\subsubsection{Why is price per weight interesting}
It is true that to study welfare, the relevant variable that would create distortions is the cost per unit. 
However, our primary aim is descriptive. 
From that point of view, transport cost schedule are expressed historically and currently in a mix per-weight and per-volume basis. 
Fo example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight’’ or ``dimensional weight). See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).
Maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors.
The existence of per-volume or per-weight shipping cost is a fact of (second) nature, directly linked to the technical constraints of the transportation sector.
The notion of per-unit shipping cost is one step removed from technical constraints and the functionning of the transportation sector.
The weight per unit is at least partly the result of a choice by firms. 
To understand the context in which they operate, we find that studying the technical per-volume or per-weight shipping cost is interesting.

Another argument is illustrated by graph \ref{graph_Share_of_discrete_goods.png}.
After computing the share of discrete goods per 5-digit sitc import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports.
According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, only over 50\% for two years.
This justifies not switching the paper from the study of price per weight to the study of price per quantity.

\begin{figure}[htbp]
	\caption{Estimated share of discrete goods in US imports, 1974-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/Share_of_discrete_goods.png}\\
		\end{tabular}
	\end{center}
	\label{graph_Share_of_discrete_goods.png}%
\end{figure}

We have in consequence then decided to maintain our original empirical strategy covering the whole period 1974-2019 in the revised version, and to extend the online Appendix with this supplementary robustness check.
We hope to convince you that this is a relevant choice. \textbf{XXX CHECK RELECTURE TO BE COMPLETED XXX}

### 2021-11-01 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
Graphique E1
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

Et sans le bilf

Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{table}[htbp]
	\caption{Comparison Price per quantity or Price per kg, 2005-2019}
	\begin{center}		
		\input{Comp_baseline_wgt_qy_reshaped.tex}
	\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

@@

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions that strongly limit both the number of sectors and of countries covered, do also impact the value of trade flows covered. In our view, this raises a non-trivial sample selection bias that may reduce the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, it is true that our method seems to yield a higher share of additive costs than when considering the price per quantity. This is somehow an expected result, as we do agree that there should be a link between the transport costs and the weight, or the volume of the goods transported. In all cases though, the share of additive costs remains substantial on average. In this respect, one might view these results as the lower bound for the size of additive costs in total transport costs.\smallskip

@@

\subsubsection{More on the Hummels's methodology}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummels's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (A) Air } & {\small (B) Vessel }\\
\multicolumn{2}{c}{{\small In percent of the export price}} \\
\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
\end{tabular}
\end{center}
\end{figure}

\textbf{XXX CHANGER legende pour transport costs, excluding composition effects; EXP/IMPORT VALUE = transport costs. On parle en \% de la valeur (y-axis) ou du prix fas (title)? XXX }

>>>>

\begin{table}[htbp]
	\caption{Comparison Price per quantity or Price per kg, 2009-2019}
	\begin{center}		
		\input{Comp_baseline_wgt_qy_reshaped.tex}
	\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

@@

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions that strongly limit both the number of sectors and of countries covered, do also impact the value of trade flows covered. In our view, this raises a non-trivial sample selection bias that may reduce the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, it is true that our method seems to yield a higher share of additive costs than when considering the price per quantity. This is somehow an expected result, as we do agree that there should be a link between the transport costs and the weight, or the volume of the goods transported. In all cases though, the share of additive costs remains substantial (except if one looks at the median fro vessel). Thus these results do not disqualify our approach, especially as our baseline estimate covers a much larger period and trade flows.\smallskip

@@

\subsubsection{More on the Hummels' methodology}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummels's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (A) Air } & {\small (B) Vessel }\\
\multicolumn{2}{c}{{\small In percent of value shipped (i.e. the export price)}} \\
\includegraphics[width=2.5in, height=1.8in]{../figure5_comme_hummels.jpg}
& \includegraphics[width=2.5in,height=1.8in]{../figure6_comme_hummels.jpg} \\
\end{tabular}
\end{center}
\end{figure}

%\textbf{XXX CHANGER legende pour transport costs, excluding composition effects; EXP/IMPORT VALUE = transport costs. On parle en \% de la valeur (y-axis) ou du prix fas (title)? XXX }
%Fait GD
